Title

### 2018-07-30 thesis/paper/paper.tex
Added non of

>>>>

\subsection{None of (Q52558054)}
The none of constraint simply forbids certain values for properties, thus effectively prohibiting certain triples, qualifiers and references. The violations, depending on nothing but specific database entries, are
\begin{equation*}
\begin{split}
\text{violation\_triple}&(S, I, \text{propertyConstant}, \text{forbiddenValueConstant}) \leftarrow \\
&\text{tripleEDB}(S, I, \text{propertyConstant}, \text{forbiddenValueConstant})
\end{split}
\end{equation*}
\begin{equation*}
\begin{split}
\text{violation\_qualifier}&(S, \text{propertyConstant}, \text{forbiddenValueConstant}) \leftarrow \\
&\text{qualifierEDB}(S, \text{propertyConstant}, \text{forbiddenValueConstant})
\end{split}
\end{equation*}
\begin{equation*}
\begin{split}
\text{violation\_reference}&(S, \text{propertyConstant}, \text{forbiddenValueConstant}) \leftarrow \\
&\text{referenceEDB}(S, \text{propertyConstant}, \text{forbiddenValueConstant})
\end{split}
\end{equation*}
